### 2025-05-28 paper-reviews/papers-2025.tex
Add ADL paper

>>>>

\section*{Simulators}
\begin{itemize}
    \item \cite{Mishra:ADL:2005}:

    Overview and classification of Architecture Description Languages (ADLs). Splits ADLs into structural (synthesis and validation oriented), behavioral (compiler and simulation oriented) and mixed. The paper includes an overview of typical workflows based on ADL. Overall it is a good reference for students to show importance and usefulness of special-purpose languages.
\end{itemize}
